### 2016-01-10 phd/sop/mrg.tex
research proposal for mrg

To learn from the best, I joined Computer Vision Lab at Samsung R\&D, where I implemented a Bag of Words-based pipeline for object classification. Consequently, I learned about the state-of-the-art in keypoint detection and feature description, which later helped me to appreciate the importance of learned low level features in convolutional neural networks. Before jumping into deep learning for object classification and image duplicate detection, I ported the project to Android and researched codebook generation within BoW. In my bachelor thesis I investigated how spatial information affects classification performance by implementing a similar system for Kinect-gathered point cloud classification.

@@

In my doctoral research project I would like to focus on deep neural networks for reinforcement learning and recurrent neural networks.

>>>>

To learn from the best, I joined Computer Vision Lab at Samsung R\&D, where I implemented a Bag of Words-based pipeline for object classification. Consequently, I learned about the state-of-the-art in keypoint detection and feature description, which later helped me to appreciate the importance of learned low level features in Convolutional Neural Networks (CNNs). Before jumping into deep learning for object classification and image duplicate detection, I ported the project to Android and researched codebook generation within BoW. In my bachelor thesis I investigated how spatial information affects classification performance by implementing a similar system for Kinect-gathered point cloud classification.

@@

In my doctoral research project I would like to focus on deep neural networks for reinforcement learning and recurrent neural networks, preferably within the Mobile Robotics Group. Following is one of the research problems that attracts me (I am also open to other problems). Suppose that a mobile robot moves through highly differentiated space with multiple scene types. High accuracy classification of hundreds of object classes requires computationally expensive approaches and huge labeled datasets \cite{imagenet}. Since some objects can be more likely to appear in a particular type of a scene, it might be possible to develop a recurrent CNN that adapts to the changing environment. One way of accomplishing this is to have the filters of the CNN tuned online in an unsupervised way, in either autoencoder \cite{autoencoders} or adversarial \cite{adversarial} setting. It would make the CNN more responsive to the recently seen object classes. It might lead to the decalibration of the final fully-connected layers of the network, which might be mitigated by simultaneous fine tuning on a (small) training set. Additionally, if the set of classes predicted by the classifier could be altered at run-time, it might be possible to achieve higher accuracy at lower computational cost. This could be implemented by having A --- a recurrent CNN fitted to the most prevalent object classes in the training set and B --- a second classifier able to predict whole groups of classes. At any given point in time A would predict a subset of all classes, while B would maintain a probability-weighted ranking of groups of classes. When a significant change in the ranking occurs, A could be refitted to the union of the most probable groups of classes.

I expect this project to take around 3 years. The first stage, lasting about 3 months, would be to develop a recurrent CNN for object classification in sequential data similar to \cite{rcnn}. The next stage would be focused on unsupervised tuning with supervised calibration of the recurrent CNN. The design of appropriate architectures, adjusting learning algorithms and merging unsupervised tuning with supervised calibration in a unified approach might take 12 to 15 months. Finally, implementing dynamically changing prediction classes requires solving a number of challenges. Refitting of the final fully-connected layers would have to be made fast enough to work in real-time, since the system should work on a mobile robot. An algorithm for scoring groups of classes and change of a scene type would have to be developed. The ultimate goal would be to cast it as a differentiable problem, so that object classes to predict could be learnt with gradient-based approach, similar to how memory is learnt in \cite{memory}. This phase might take around 15 months.
